Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-13 ms.tex
added HEALPix reference

\section{Pixelization}
For the purpose of fitting, we break the sky into independent pixels of 
angular diameter $\sim$, defined by the HEALPix pixelization with nside=2048. 
This is convenient because the Planck maps are provided in this format and 
this pixelization adequately samples the $6.1'$ resolution maps under 
consideration. We reiterate that each pixel is fit independently of 
neighboring pixels.

>>>>

\section{Pixelization}
For the purpose of fitting, we break the sky into independent pixels of 
angular diameter $\sim$, defined by the HEALPix pixelization with nside=2048 \citep{healpix}. 
This is convenient because the Planck maps are provided in this format and 
this pixelization adequately samples the $6.1'$ resolution maps under 
consideration. We reiterate that each pixel is fit independently of 
neighboring pixels.
